|

### 2021-08-16 article/article.Rmd
Preliminary Compilation Article

\begin{figure}[htb!]
  \begin{center}
  \caption{Legislation Approved in Municipalities Closer to the City Council Thresholds}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{figs/laws2019.pdf}}
      \bigskip
      \label{LEGAPPR}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
  \caption{Electoral Attractiveness of Councilor's Activities and Practices}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{figs/elecYieldJobsCouncilorsJan2019.pdf}}
      \bigskip
      \label{survelec}
    \end{minipage}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htb!]
  \begin{center}
  \caption{Legislation Approved in Municipalities Closer to the City Council Thresholds}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/lawsApproved.pdf}}
      \bigskip
      \label{LEGAPPR}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
  \caption{Electoral Attractiveness of Councilor's Activities and Practices}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/elecYieldJobsCouncilors.pdf}}
      \bigskip
      \label{survelec}
    \end{minipage}
  \end{center}
\end{figure}
